---
title: "[PROJECT TITLE]: Analysis Summary"
author: "[YOUR NAME]"
date: today
format:
  gfm:
    toc: true
    fig-width: 7
    fig-height: 4
execute:
  echo: false      # hide code; note this does NOT hide output
  warning: false
  message: false
---

```{r setup}
source(here::here("code", "00_setup.R"))
dat <- readRDS(file.path(path_processed, "derived.rds"))
```

<!--
BEFORE YOU COMMIT THIS REPORT, check reports/README.md.

The short version: this file is tracked by Git, so whatever your chunks print
ends up in the repository permanently. A `head(dat)` left in from debugging
puts participant rows into a document that looks like a summary.

`echo: false` above hides your CODE. It does not hide your OUTPUT.
-->

## Summary

Two or three sentences a busy PI could read and understand. Lead with what you
found, not with what you did.

## Sample

```{r sample}
#| label: tbl-sample
#| tbl-cap: "Analytic sample"

# Report aggregate counts only -- never one row per participant.
# dat |>
#   summarize(
#     n         = n(),
#     mean_age  = round(mean(age, na.rm = TRUE), 1),
#     pct_female = round(100 * mean(gender == "Female", na.rm = TRUE), 1)
#   ) |>
#   knitr::kable()
```

[n] participants, after excluding [n] for [reason]. Exclusion criteria and
their justification are logged in
[`../docs/decisions.md`](../docs/decisions.md).

## Main findings

```{r primary}
#| label: fig-primary
#| fig-cap: "[Descriptive caption]"

# ggplot(dat, aes(x = condition, y = outcome)) +
#   stat_summary(fun = mean, geom = "col") +
#   stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
#   labs(x = "Condition", y = "Outcome") +
#   theme_minimal()
```

Describe what the figure shows in words. A reader should get the finding from
the prose even if they skip the figure.

## Model results

```{r model}
#| label: tbl-model
#| tbl-cap: "Regression results"

# model <- lm(outcome ~ condition + age, data = dat)
# broom::tidy(model, conf.int = TRUE) |>
#   mutate(across(where(is.numeric), \(x) round(x, 3))) |>
#   knitr::kable()
```

Report the estimate, its uncertainty, and what it means substantively. A
coefficient without an interpretation is not a finding.

## Caveats

What this analysis cannot tell you. Write this section honestly and early —
it is the part a partner organization most needs and least often gets.

---

*Generated from `reports/summary.qmd`. Analysis code in `code/`. Rendered
`r format(Sys.Date(), "%Y-%m-%d")`.*
